Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-23 paper/icml_drau/advup.tex

\begin{theorem}
Under suitable smoothness assumptions, $A^\pi_\deltat(s,a)$ has a limit
$A^\pi(s,a)$ when $\deltat\to 0$. The limit is informative about
actions, namely, if a policy $\pi'$ satisfies $V^{\pi'}>V^{\pi}$ for all states, then
$A^\pi(s,\pi'(s))>0$ for some $s$.
\end{theorem}

@@

\subsection{Scaling the Learning Rates}
\label{subsec:lr}
\input{pendulum_fig.tex}
\TODO{
For the algorithm to admit a continuous-time limit, the discrete-time trajectories
of parameters must converge to well defined trajectories as $\deltat$ goes to
$0$.
% The optimization steps should not be too large,
% in which case parameter trajectories could jump in a single gradient step,
% or too small, in which case the trajectories would become stationary as
% $\deltat$ goes to $0$.
This in turn imposes conditions on the scalings of the
learning rates of algorithms robust to changes of the time discretization.
}

>>>>

\begin{theorem}
Under suitable smoothness assumptions, $A^\pi_\deltat(s,a)$ has a limit
$A^\pi(s,a)$ when $\deltat\to 0$. The limit is informative about
actions: namely, if a policy $\pi'$ strictly dominates $\pi$, 
%satisfies $V^{\pi'}>V^{\pi}$ for all states,
then
$A^\pi(s,\pi'(s))>0$ for some state $s$.
\end{theorem}

@@

\subsection{Scaling the Learning Rates}
\label{subsec:lr}
\input{pendulum_fig.tex}
\TODO{
For the algorithm to admit a continuous-time limit, the discrete-time trajectories
of parameters must converge to well-defined trajectories as $\deltat$ goes to
$0$.
% The optimization steps should not be too large,
% in which case parameter trajectories could jump in a single gradient step,
% or too small, in which case the trajectories would become stationary as
% $\deltat$ goes to $0$.
This in turn imposes precise conditions on the scalings of the
learning rates.}% of algorithms robust to changes of the time discretization.  }
